CTest Integration of Sikuli Automated GUI Testing

### 2011-06-17 Documentation/Article.tex
Working on Intro

\begin{abstract}
\noindent 
\end{abstract}

@@

\tableofcontents
% ------------------------------------------------------------------------
\section{Introduction}

% ------------------------------------------------------------------------
\section{Sikuli}

>>>>

\begin{abstract}
\noindent

\end{abstract}

@@

\tableofcontents
% ------------------------------------------------------------------------
\section{Introduction}
GUI testing is a key aspect of software development. Having a well defined testing protocol is very
important in maintaining a productive flow, especially on the eve of a new release.  The number of units
to test is greatly compounded as the software becomes more complex and keeping up with the complexity can be
immensely time consuming.  We collected a list of over 400 different but very repetitive GUI tests which
involved endless clicking and checking.  This task took around 5 hours to complete each time a new release was ready.
Then debugging would push release dates back days or even weeks.   
% ------------------------------------------------------------------------
\section{Sikuli}
